I have checked your code and I when compare with the alternative code that I made using "dplyr" package the results are the same.

Here is the alternative code using "dplyr" package:
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(magrittr)
library(xtable)
library(stringi)
library(tidyr)

```




```{r results='asis', echo=FALSE, include=FALSE,}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE)
```
#formating tables
```{r}
library(xtable)
```
#data wrangling
```{r}
library(dplyr)
```
#text processing
```{r}
library(stringi)
```





#Read the data
```{r}
dat <- read.csv("ArrestMini.csv")
```



#Create new variables: "DATE" and "TIME" from variables "ARRESTTIME"
```{r}
dat1 <- dat %>% 
  separate(ARRESTTIME, c('DATE', 'TIME'), sep = 'T')
```

#Aggregate council districts that is affected by crime on the day --> I save it as "Arrest_Daily"
```{r}
Arrest_Daily <- dat1 %>%
  mutate(Date = as.Date(DATE, "%m/%d/%Y")) %>%
  group_by(DATE) %>%
  summarize(CASES = n(), NUM_COUNCIL = n_distinct(COUNCIL_DISTRICT)) %>%
  arrange(DATE) 
```

#View Arrest_Daily
```{r}
Arrest_Daily
```

#Plot
```{r}
RDATE <- as.Date(Arrest_Daily$DATE)
fix(RDATE)
plot(RDATE, Arrest_Daily$NUM_COUNCIL, type="l", col="red", xlab = "TIME", main = "Number of council districts that is affected by cirime", ylab = "Number of Council")

```



